Stochastic Variance Reduced Policy Gradient

### 2018-02-02 svrpg.tex
correzioni

These two weights ${\bf{\it N}}$ and ${\bf{\it B}}$ represent, respectively, the number of trajectories used for a snapshot and the number of trajectories used for an update of the parameters in a sub-iteration. Therefore, in this stopping condition, we use them to take into account the trajectories efficiency. The less trajectories we use to perform an update the better it is from a data usage point of view, hence we want to facilitate sub-iterations with respect to snapshots.

>>>>

These two weights ${\bf{\it N}}$ and ${\bf{\it B}}$ represent, respectively, the number of trajectories used for a snapshot and the number of trajectories used for an update of the parameters in a sub-iteration. Therefore, in this stopping condition, we use them to take into account the trajectories efficiency. The less trajectories we use to perform an update, the better it is from a data usage point of view. Hence we want to facilitate sub-iterations with respect to snapshots.
